---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"cointoss"` is a minimal [R](http://www.r-project.org/) package 
that provides functions to simulate tossing a coin.

* `coin()` creates a coin object (of class `"coin"`)
* `toss()` tosses a coin object, producing a `"toss"` object.
* `plot()` method for a `"toss"` object to plot frequencies of heads.
* `summary()` method for a `"toss"` object.


## Motivation

This package has been developed to illustrate some of the concepts
behind the creation of an R package.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 

# install "cointoss" (without vignettes)
devtools::install_github("gastonstat/cointoss")

# install "cointoss" (with vignettes)
devtools::install_github("gastonstat/cointoss", build_vignettes = TRUE)
```


## Usage

```{r}
library(cointoss)

# default coin
coin1 <- coin()
coin1

# 1 toss of coin1
toss(coin1)

# 10 tosses of coin1
toss10 <- toss(coin1, times = 10)
toss10

# summary
summary(toss10)


# 100 tosses
toss100 <- toss(coin1, times = 100)

# summary
summary(toss100)
```
